---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rmiss

<!-- badges: start -->
<!-- badges: end -->

The goal of rmiss is to help visualize missing vales in data frames. This package contains a convenience function to make a ggplot to visualize the proportion of missing values for all or selected columns in a given data frame.

## Installation

You can install the development version of rmiss from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/rmiss", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to use the `plot_missing_values_proportions()` function to visualize the proportion of missing values for all columns in a data frame called *airquality*.

```{r example1}
library(rmiss)
# Create the plot for all variables in airquality (a dataset in Base R)
plot_missing_values_proportions(df=airquality, point_color = 'darkgreen', line_color = 'darkgreen')
```


We can also choose to visualize the proportion of missing values for some selected columns in the *airquality* dataset by specifying column names using the `vars` argument.

```{r example2}
plot_missing_values_proportions(df=airquality, vars = c(Ozone, Wind, Temp))
```

